### 2016-10-28 thesis/intro/intro.tex
tmp commit

\citep{Gelber2008, Lee2008, Yusuf2005}

@@

In addition to this, the worldwide prevalence of childhood overweight and obesity has been increasing steadily since 2000 \citep{WHO2014}.
Furthermore, the prevalence of overweight in children under 5 years was estimated to reach from 6.3\% in 2013 to 11\% by 2025 if the current trend continued \citep{WHO2014}.
Although the current obesity status of the adult population sounds daunting, the fact that more of the younger population who are overweight and obese poses a much greater risk for the health of the population.

@@

Even though some individual-level factors are involved with obesity, it is clear that these individual-level factors cannot be accounted for the global epidemic of obesity that the world observes.
For this reason, obesity is thought to be caused mainly by the environmental factors that are present in the population.

The first key factor that contirbutes to the global rise in obese population is the availability and abundance of certain food in the country.

\textit{(Expand on this -- better trades around the globe (?)) \citep{Kearney2010, Malik2013}}

The second factor to consider is the behavioural changes led by the urbanisation of the population.
\textit{(Expand on this -- physical activity, sociocultural norm, etc.\citep{Malik2013})}

The third factor is the income and socioeconomic status of the countries.
\textit{(Expand on this -- rise in income, availability of health care, etc.\citep{Malik2013})}

The last factor, which ties in strongly with the first key factor, is the choice of diet by the population.
\textit{(Expand on this -- increased variety of food, low quality and high energy food choice, etc.)}

>>>>

possible papers:\citep{Gelber2008, Lee2008, Yusuf2005}

@@

In addition to this, the worldwide prevalence of childhood overweight and obesity has been increasing steadily since 2000 \citep{WHO2014}.
Furthermore, the prevalence of overweight in children under 5 years was estimated to reach from 6.3\% in 2013 to 11\% by 2025 if the current trend continued \citep{WHO2014}.
The current obesity status of the adult population is bad already, but the fact that more of the younger population who are overweight and obese poses a much greater risk for the health of the population (discussed in \cref{sub:impact_of_obesity}).

@@

Even though some individual-level factors are involved with obesity, it is clear that these individual-level factors cannot be accounted for the global epidemic of obesity that the world currently observes.
For this reason, obesity is thought to be caused mainly by the environmental factors that are present in the population.\\

\noindent
The first key factor that contirbutes to the global rise in obese population is the availability and abundance of certain food in the country.
With the help from government trade policies, food and other goods have become easier to trade between the country, helping the economic growth of many countries around the world (citation -- Kearney?).
This led to greater abundance of food in general, greater number of choices of food and shifted the overall nutritional status of the country \citep{Malik2013}.
This shift in the food choice and availability (and the economic benefit associated with the trades) had a positive impact on the country, but the growth in the food market also resulted in a different, much larger problem -- obesity.

As an example, in the \gls{usa}, the cost of corn and soy is low due to the fact that they are the raw ingredients for most processed food and beverages, such as high fructose corn syrups used to sweeten many soft drinks in the \gls{usa} \citep{Malik2013}.
Moreover, corn and soy are also the main food for the livestock, which results in lower prices for meat \citep{Malik2013}.
On the othere hand, the prices of fruits and vegetables remain expensive due to the lack of support by the government to lower the cost associated with the production (more citation...) \citep{Malik2013}.

As a result, more people are inclined to consume food that are cheap, have little nutritional value and high in energy, than the food that are expensive, nutritional and healthy alternatives.
Thus, the population is more likely to become obese by making worst food choice.\\

\noindent
The second factor to consider is the behavioural changes led by the urbanisation of the population.

\textit{(Expand on this -- physical activity, sociocultural norm, etc.)}
\citep{Malik2013}\\

\noindent
The third factor is the income and socioeconomic status of the countries.
\textit{(Expand on this -- rise in income, availability of health care, etc.)}
\citep{Malik2013}\\

\noindent
The last factor, which ties in strongly with the first key factor, is the choice of diet by the population.
\textit{(Expand on this -- increased variety of food, low quality and high energy food choice, etc.)}
